### 2015-03-04 paper_40_cri.tex
defined the requirements element, so finished chapter 4

                Then $S_1$ represents the quality score for that given time period.

@@

                \begin{itemize}
                    \item $A_{a_i}$ actual availability for System ID $i$
                    \item $A_{e_i}$ expected availability for System ID $i$
                \end{itemize}

@@

                \[
                    S_{2} = \sum\limits^n_{i=1} w'_i S_{2_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]

@@

                \begin{itemize}
                    \item $a_{ij}$ answer to question $i$ for respondent $j$
                    \item $n$ number of questions
                    \item $m$ number of respondents
                    \item $min$ minimum score for a question
                    \item $max$ maximum score for a question
                \end{itemize}

@@

                \[
                    S_{3} = \sum\limits^n_{i=1} w'_i S_{3_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]

@@

                \[
                    S_{4_i} = 2k \cdot (C.D.F.(\Delta_i) - \frac{1}{2})
                \]

@@

                \[
                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]

@@

        \subsubsection{REQUIREMENTS}
            The requirements of a software development organization are important.

            \begin{description}
              \item[Function Points] find a definition and a comparison with story points
              \item[Story Points] Look in some agile book
            \end{description}

            \paragraph{REQUIREMENTS DATA}

@@

            \paragraph{REQUIREMENTS FORMULA}
                Requirements are desired new features or enhancements 
                to a software product.  It is important to know how many requirements
                were scheduled to be completed versus how many actually got completed.  
                \[
                    S_5 = \frac{\sum^n_{i=1}\left( R_{a_i} - R_{e_i} \right)}{n}
                \]
                \begin{itemize}
                    \item $R_a$ actual requirements completed for application $i$
                    \item $R_e$ expected requirements completed for application $i$
                \end{itemize}

@@

            \[
                CRI =\sum\limits^n_{i=1} w_i S_i \text{ where } \sum\limits^n_{i=1} w_i = 1
            \]

>>>>

                Then $S_1$ represents the CRI quality score for that given time 
                frequency.

@@

                \begin{itemize}
                    \item $S_{2_i}$ is the availability score for System ID $i$
                    \item $A_{a_i}$ actual availability for System ID $i$
                    \item $A_{e_i}$ expected availability for System ID $i$
                \end{itemize}

@@

                \[
                    S_{2} = \sum\limits^n_{i=1} w'_i S_{2_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]
                where $S_2$ is the CRI availability score for the time frequency.

@@

                \begin{itemize}
                    \item $S_{3_i}$ is the satisfaction score for Question ID $i$
                    \item $a_{ij}$ answer to question $i$ for respondent $j$
                    \item $n$ number of questions
                    \item $m$ number of respondents
                    \item $min$ minimum score for a question
                    \item $max$ maximum score for a question
                \end{itemize}

@@

                \[
                    S_{3} = \sum\limits^n_{i=1} w'_i S_{3_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]
                where $S_3$ is the CRI satisfaction score for the time frequency.

@@

                \[
                    S_{4_i} = 2k \cdot (C.D.F.(\Delta_i) - \frac{1}{2})
                \]
                where
                \begin{itemize}
                    \item $S_{4_i}$ is the schedule score for Project ID $i$
                \end{itemize}

@@

                \[
                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]
                where $S_4$ is the CRI schedule score for the time frequency.

@@

        \subsubsection{REQUIREMENTS}
            The requirements of an SDO are important. Requirements are desired 
            new features or enhancements to a software product.  It is important
            to know how many requirements
            were scheduled to be completed versus how many actually got completed. 
            They provide a measurement
            of the amount of work being completed. However, not all requirements
            are created equal.  Some requirements can be quickly and easily
            implemented while other requirements will take much longer.  It
            is often difficult to know the challenges ahead of time.  Due to
            this uncertainty, estimating
            the number of requirements a team can complete in a given time frame can
            be difficult. Thus, number of requirements is one way to measure 
            amount of work
            but there are others.  Here are 3 possible choices in descending
            order of preference.
            \begin{description}
                \item[Function Points] Function points measure the size of the
                    software functionality, not the size or time required
                    to implement the functionality \cite{Jensen2014}.  
                    If done properly,
                    function points will provide the most concise measurement
                    for amount of work being completed. 
                \item[Story Points] Story points, sometimes just referred to 
                    as stories, are broken down requirements that can be
                    completed in an Agile Sprint of 2 to 4 weeks.  A 
                    story is usually smaller, simpler, and more concise
                    that a plain requirement. 
                    Unfortunately, these only apply to an
                    SDO using the Agile methodology, specifically 
                    Scrum \cite{Ashmore2014}.
                \item[Requirements] These are just the requirements as
                    written by the users or business partners.  Each requirement
                    can vary greatly from another requirement.  Estimating
                    number of requirements can be a difficult if not impossible
                    task.  
            \end{description}

            To summarize, this element is not completely a measurement of requirements
            but rather a measurment of the work being completed.

            \paragraph{REQUIREMENTS DATA}
                Table \ref{tab:req} specifies the data required to compute
                a score for the requirements element of CRI.  Again,
                scheduled requirements and actual requirements can also 
                be a count of story points or function points.  All of 
                the columns are required. The data collected is the
                frequency date and then the number of requirements scheduled
                to be completed and the actual number of requirements completed.

@@

            \paragraph{REQUIREMENTS FORMULA}
                The requirements formula is the percentage above or below the
                scheduled number of requirements. Requirements have a nice
                lower bound of 0 since negative requirements cannot be 
                completed\footnote{Theoritically, a negative requirement would
                be considered a defect.}.  Unforntunately, an upper bound
                does not exist.  The variablity of requirements is not
                as large as the variability of the number of defects, so
                a simpler strategy can be used.  For requirements, a 
                multiplier $b$ will be used to find the upper bound. The
                number of scheduled requirements should be multiplied by
                $b$ to obtain the upper bound.  The value of $b$ should
                be determined by looking at the historical data to make sure
                no number of completed requirements will exceed $b$ times
                the number of scheduled requirements. An example will be shown
                in Section \ref{sec:case-req}. Common choices for $b$ will be 1
                and 2. Also, the formula will be
                created to deal with a value going above the upper bound.

                \begin{displaymath}
                   S_{5_i} = \left\{
                     \begin{array}{lr}
                       \text{where } R_{a_i} > b \times R_{s_i} & :  1 \times k \\
                       \text{where } R_{a_i} \leq R_{s_i} & : \left[ \frac{R_{a_i} - R_{s_i}}{R_{s_i}}\times k \right] \\
                       \text{where } R_{a_i} > R_{s_i}  & : \left[ \frac{R_{a_i} - R_{s_i} }{b \cdot R_{s_i}}\times k \right]
                     \end{array}
                   \right. \text{   , calculate requirements score for each project $i$}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $S_{5_i}$ is the requirements score for Project ID $i$
                    \item $R_{a_i}$ actual requirements completed for Project ID $i$
                    \item $R_{s_i}$ expected requirements completed for Project ID $i$
                    \item $b$ multiplier to determine the upper bound
                \end{itemize}
                Then the requirements score is calculated as below.  
                Use a weighted average to combine the requirements scores
                from the Project IDs.

                \[
                    S_{5} = \sum\limits^n_{i=1} w'_i S_{5_i} \text{ where }
                        \sum\limits^n_{i=1} w'_i = 1
                \]

                where $S_5$ is the CRI requirements score for the time frequency.

@@

            \[
                CRI =\sum\limits^n_{i=1} w_i S_i 
                    \text{ where } \sum\limits^n_{i=1} w_i = 1
            \]
            where
            \begin{itemize}
                \item $CRI$ is the overall CRI score for the time frequency
            \end{itemize}

            This weighted average allows for a score to be computed even when not
            all 5 elements are present. Just perform the weighted average with
            as many elements as present.  This technique allows CRI to implemented
            before data for all the elements has been collected.  Just begin
            to average elements as they become accessible.

### 2015-03-04 paper_70_case-study.tex
update sensitivity description
defined the requirements element, so finished chapter 4

        \subsubsection{SCHEDULE}
        \subsubsection{REQUIREMENTS}
        \subsubsection{OVERALL}
            All of the months do not include the same elements.

>>>>

        \subsubsection{SCHEDULE}
        \subsubsection{REQUIREMENTS}
        \label{sec:case-req}
            There were 15 rows of data that contained 0 for both
            scheduled and actual
            \begin{longtable}{@{}l rr rrr}
                \toprule%
                 \centering%
                 {\bfseries Column}
                 & {\bfseries Min}
                 & {\bfseries Max}
                 & {\bfseries Median}
                 & {\bfseries Mean}
                 & {\bfseries Variance} \\

                Scheduled & 0 & 1.0 & 1.0 & 0.9745 & 0.023 \\
                \myrowcolour%
                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\
                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\

                \multicolumn{6}{c}{476 obs. from 402 Project IDs from 2010 to 2015} \\

                \caption{REQUIREMENTS DATA DESCRIPTIVE STATISTICS}
                \label{tab:requirements_desc}
            \end{longtable}

            The multiplier $b$ is set to 1 because none of the historical performance
            ever exceeded 25\% more requirements than scheduled. Thus the upper
            bound is the number of schedule requirements plus $b=1$ times
            the number of scheduled requirements, for an upper bound of twice
            the scheduled requirements.

        \subsubsection{OVERALL}
            All of the months do not include the same elements.
